Sustainable behaviour

### 2020-11-29 03-comportements.Rmd
TPB

---

@@

- @Ajzen1991 developed **Theory of Planned Behaviour (TPB)**  which is one of the most influencing model for designing behavioral interventions [@Yuriev2020]. Therefore, researchers have been increasingly employing the TPB model across various disciplines including environmental science and sustainability management
TPB postulates considers three main aspects (1) attitude towards behavioral intention, (2) subjective norms, and (3) perceived behavioral control (PCB),  together they shape behavioral intention as well as actual behavior.  To date, TPB has received around 90,000 citations [@Yuriev2020]

@@

```{r}

```

>>>>

---
```{r}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
```

@@

- @Ajzen1991 developed **Theory of Planned Behaviour (TPB)**  which is one of the most influencing model for designing behavioral interventions [@Yuriev2020]. Therefore, researchers have been increasingly employing the TPB model across various disciplines including environmental science and sustainability management
TPB postulates considers three main aspects

1.  Attitude towards behavioral intention, 
2. Subjective Norms (SN), and 
3. Perceived Behavioral Control (PCB),

together they shape behavioral intention as well as actual behavior.  To date, TPB has received around 90,000 citations [@Yuriev2020]

```{r, include=TRUE, echo=FALSE}

mermaid("
graph LR
  A[\"Attitude toward the act (Att)\"]-->D[Behavioural Intention]
  B[\"Subjective Norm (SN)\"]-->D[Behavioural Intention]
  C[\"Perceived Behavioural Control (PBC)\"]-->D[Behavioural Intention]
  D[Behavioural Intention]-->E[Behaviour]
  C[Perceived Behavioural Control]-.->E[Behaviour]

  classDef className font-size:20px;
  class A,B,C,D className;
")
```

@@

```{r}
TPB <- 
tribble(
  ~Variable, ~Definition, ~Definition.recycling,
  "Attitude", 
    "Attitude toward the behavior and refers to the degree to which a person has a favorable or unfavorable evaluation or appraisal of the behavior in question",
      "The extent to which plastic recycling is valued by people, whether positive or negative",

  "Subjective Norms",
   "The perceived social pressure to perform or not to perform the behavior",
      "The extent to which people are influenced by perceived norms of plastic recycling in their  surroundings",

  "Perceived Behavioral Control (PCB)",   
    "The perceived ease or difficulty of performing the behavior and it is assumed to reflect past experience as well as anticipated impediments and obstacles", 
        "the perceived power (and knowledge) of people to implement plastic recycling",

  "Behavioral intention",   
    "They are indications of how hard people are willing to try, of how much of an effort they are planning to exert, in order to perform the behavior",
    "A perceived likelihood or subjective probability of decision makers that they will implement plastic recycling in their organizations",

  "Behaviour", 
    " ",
      "The extent to which organizations have implemented best practices of plastic recycling"
)
```

```{r, include=TRUE}

kbl(TPB) %>%
  kable_paper(full_width = F)
```
